Supplementary Material for 'New insights into the Weddell Sea ecosystem applying

### 2023-10-26 Manuscript/Manuscript.Rmd
Interquartile range IS

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Frequency distribution of interaction strengths for the Weddell Sea food web. Total number of interactions = 16041. The distribution was best fitted to a ‘gamma’ model."}
knitr::include_graphics("Fig3_IntDist.png")
```

>>>>

```{r, out.width = "12cm", echo = FALSE, fig.cap = "interquartile range for the estimated interaction strengths of the Weddell Sea food web. Total number of interactions = 16041."}
knitr::include_graphics("Supp1_IQR.png")
```

### 2023-10-26 Manuscript/SupMaterial.Rmd
Interquartile range IS

As the resource density $X_R$ is not known we estimated it according to the equation S18 and supplementary figures 2i & j (individuals/m2 - m3)

@@

were $p_x$ is -0.79±0.08 for 2D and -0.86±0.07 for 3D.

@@

The statistical distribution that best fitted the empirical interaction strength distribution was a ‘gamma’ due to the skew towards weaker interactions. Gamma parameters are: shape = 2.699e-1 and scale = 2.008e+4. Table 3 shows the results for the six candidate models used.

@@

load("../Manuscript/ModelFit.rda")
knitr::kable(IS_fit %>% arrange(., deltaAIC), digits = c(0,0,2,2), col.names = c("Model", "df", "AIC", "deltaAIC"), caption = "Model comparison for the distribution of interaction strengths of the Weddell Sea food web. Order by best fit. References: df = degrees of freedom, AIC = Akaike Information Criterion, deltaAIC = difference with best fit. Log-Normal is the best model.")

>>>>

As the resource density $X_R$ is not known for our study case we estimated it according to the equation S18 and supplementary figures 2i & j (individuals/m2 - m3) from @Pawar2012:

@@

where $p_x$ is -0.79±0.08 for 2D and -0.86±0.07 for 3D.

### Interaction Strength variability

With the aim of taking into account the variability of the exponents in $\alpha$ and $X_R$ estimations, we run 1000 simulations for calculating each pairwise predator-prey interaction. Due to the skewness nature of the estimated interaction distributions, we considered the median as the summarizing value. Such a skewness is shown in the following histogram for the interquartile range:

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Frequency distribution of interquartile range for the estimated interaction strengths of the Weddell Sea food web. Total number of interactions = 16041."}
knitr::include_graphics("Supp1_IQR.png")

@@

The statistical distribution that best fitted the empirical interaction strength distribution was a ‘log-Normal’ due to the skew towards weaker interactions. Table 3 shows the results for the six candidate models used.

@@

load("../Results/ModelFit_sim.rda")
knitr::kable(IS_fit_sim %>% arrange(., deltaAIC), digits = c(0,0,2,2), col.names = c("Model", "df", "AIC", "deltaAIC"), caption = "Model comparison for the distribution of interaction strengths of the Weddell Sea food web. Order by best fit. References: df = degrees of freedom, AIC = Akaike Information Criterion, deltaAIC = difference with best fit. Log-Normal is the best model.")
